Weather classification using Convolutional Neural Networks

### 2020-01-09 msc_english_contents.tex
Change table of contents

\chapter{Survey of approaches to similar problems}
How did the others do
\section{Non-neural}
Some cool old school pixel approaches
\section{CNN / Pretrained CNN}
How did they train their model
\section{Video}
How to use video

\chapter{Neural networks}
Yes go through CNN, LSTM, Attention
\section{Convolutional Neural Networks}
CNN VERY COOL THING

\subsection{Transfer learning}
How to transfer learning
\subsection{ResNets and VGGNets and other architectures}
Describe them
\section{Recurrent Neural Networks}
LSTMs extremely cool
\subsection{Combining in video}
Video very cool
\section{Attention}
Attention huh

\chapter{Dataset}
Describing our data
\section{Semi-supervised learning}

>>>>

\chapter{Neural networks}
Yes go through CNN, LSTM, Attention
\section{Convolutional Neural Networks}
CNN VERY COOL THING now if you need some help here I am
\subsection{Neural image processing}
How it different from classical and why it works
\subsection{Transfer learning}
How to transfer learning
\subsection{ResNet}
Describe them
\subsection{EfficientNet}
Describe them
\subsection{Image classification}
Tough problem ::)
\section{Image embedding}
pretty amazing
\section{Recurrent Neural Networks}
LSTMs extremely cool
\subsection{Recurrent networks over embeddings}
How dat works
\subsection{Video classification}
Video very cool
\section{Attention}
Attention huh
\section{Multi-task learning}
What it do
\chapter{Related Work}
How did the others do and me also
\section{Non-neural}
Some cool old school pixel approaches
\section{CNN / Pretrained CNN}
How did they train their model
\section{Video}
How to use video\cite{guerra_weather_2018}
\chapter{Dataset}
Describing our data
\section{Data format}
\section{Data processing and labeling}
\section{Semi-supervised learning}
